Investigating the Effect of Dataset Representivity for Image Colourisation

### 2019-10-08 Paper/paper.tex
Added images and bibtex

\documentclass[conference]{IEEEtran}
% \IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

To make our lives easier, instead of using the typical RGB color space, we use the CIELAB color space. This makes it convenient when seperating the gray and color channels due to the fact that the 'L' channel in LAB is simply the grayscale image. We can then pass this grayscale input (1xWxH) through our model and compare the output (2xWxH) to the original 'AB' channels of the image. These 'AB' channels make up the color and simply show the red-green and blue-yellow shift respectively. HSB would be another option when choosing a suitable colour space. In general, the choice of colour space makes no difference to the resulting image that our network produces.

@@

@@

Our choice of model has been based on the simple regression model developed by Luke Melas and loosely based on the network used by Zhang et al. with the major difference being that their model used in 'Colorful Image Colorization' approached colorization as a classification problem.

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEfull,colourisation}

>>>>

\documentclass[conference]{IEEEtran}
% \IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{textcomp}
\usepackage{subfig}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

To make our lives easier, instead of using the typical RGB color space, we use the CIELAB color space. This makes it convenient when seperating the gray and color channels due to the fact that the 'L' channel in LAB is simply the grayscale image. We can then pass this grayscale input (1 x W x H) through our model and compare the output (2 x W x H) to the original 'AB' channels of the image. These 'AB' channels make up the color and simply show the red-green and blue-yellow shift respectively. HSB would be another option when choosing a suitable colour space. In general, the choice of colour space makes no difference to the resulting image that our network produces.

@@

\begin{figure}[h!]
    \centering
    \subfloat[Regression]{{\includegraphics[width=3.5cm]{cham-reg} }}%
    \qquad
    \subfloat[Classification]{{\includegraphics[width=3.5cm]{cham-class} }}%
    \caption{Colour generated using regression vs classification \cite{zhang2016colorful}}%
    \label{fig:reg_vs_class}
\end{figure}

@@

Our choice of model has been based on the simple regression model developed by Luke Melas and loosely based on the network used by Zhang et al. \cite{zhang2016colorful} with the major difference being that their model used in 'Colorful Image Colorization' approached colorization as a classification problem.

@@

\medskip

\bibliographystyle{ieeetr}
\bibliography{bibfile}
